---
title: "C11 structural bioinfo P1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

Q1: Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” >
“by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project and determine the percentage of structures solved by X-Ray and Electron Microscopy. From the website what proportion of structures are protein? 
(Aim to have a rendered GitHub document with working code that yields your answers)

```{r}
f <- read.csv("Data Export Summary.csv", , row.names = 1, header = TRUE, sep = ",")
f
f$Total/sum(f$Total)
proteinProp <- f[,2]/(f[,3]+f[,2]+f[,4])*100
proteinProp # percentage
```

```{r}
percent.by.method <- f$Total/sum(f$Total)*100
names(percent.by.method) <- rownames(f)
percent.by.method
#X-ray popular vs low popularity now electron microscopy
```
```{r}
sum(f$Proteins)/sum(f$Total) * 100
```
Q2: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?
**822 within currently showing **
Total 2880
 1138 search within bar

1HSG: breakthrough
VMD display

Q3: Water molecules normally have 3 atoms. Why do we see just one atom per water molecule in this structure?
because water have polar covalent bond and only the most electron place is shown in circle. 
not protein and not water and show class 1 HIV drug
licorice fit in to surf_Protein

## 3.1 getting started with bio3d Doing 1hsg in R
```{r}
library(bio3d)
pdb <- read.pdb("1hsg.pdb") # get the pdb input
pdb
attributes(pdb)
#attributes( + attr: )
head(pdb$atom)
pdb$atom # all data
pdb$atom$resid # all aa
aa321(pdb$atom$resid) #single letter with warning sequece
```
Q6. How many amino acid residues are there in this pdb object and what are the two nonprotein residues?
# there are 198 residues from summary

## 3.5atom selection

```{r}
ca.inds<- atom.select(pdb, "calpha")
ca.inds
head(pdb$atom[ca.inds$atom,]) # subset of atom

```
## how write just protein and and drug only parts of these molecular PDB files
```{r}
#li:ligand, pr:protein
#skipping download if you read file again(waste of time)
#temp<-bio3d::write.pdb()
ca.inds<- atom.select(pdb, string = "calpha") #can just "___"(w/o string)
pr.inds<- atom.select(pdb, string = "protein")
li.inds<- atom.select(pdb, string = "ligand")
li.inds
pdb$atom[pr.inds$atom,]
head(pdb$atom[pr.inds$atom,]) # prints out all protein bits
pr.pdb <- trim.pdb(pdb, pr.inds)
li.pdb <- trim.pdb(pdb, li.inds)
write.pdb (pr.pdb, file = "protein.pdb") # parse out protein to pdb
write.pdb (li.pdb, file = "ligand.pdb") #parse out ligands.pdb
#can drag output to VMD
```

## bio3d view
###
#temp package not that available
'''
install.packages("devtools")
devtools::install_bitbucket("Grantlab/bio3d-view")

library("bio3d.view")
pdb<-read.pdb("5p21")
'''
#view(pdb, "overview")
#view(pdb,"overview",col="sse")
##ec part

Optional: Generate and save a figure clearly showing the two distinct chains of HIV-protease along with the ligand. You might also consider showing the catalytic residues ASP 25 in each chain (we recommend Licorice for these side-chains). Email this figure to bjgrant@ucsd.edu for grading.
Discussion Topic: Can you think of a way in which indinavir, or even larger ligands and substrates, could enter the binding site?
