---
title: "C11 structural bioinfo P1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

Q1: Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” >
“by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project and determine the percentage of structures solved by X-Ray and Electron Microscopy. From the website what proportion of structures are protein? 
(Aim to have a rendered GitHub document with working code that yields your answers)

```{r}
f <- read.csv("Data Export Summary.csv", , row.names = 1, header = TRUE, sep = ",")
f
f$Total/sum(f$Total)
proteinProp <- f[,2]/(f[,3]+f[,2]+f[,4])*100
proteinProp # percentage
```

```{r}
percent.by.method <- f$Total/sum(f$Total)*100
names(percent.by.method) <- rownames(f)
percent.by.method
#X-ray popular vs low popularity now electron microscopy
```
```{r}
sum(f$Proteins)/sum(f$Total) * 100
```
Q2: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?
**822 within currently showing **
Total 2880
 1138 search within bar

1HSG: breakthrough
VMD display

Q3: Water molecules normally have 3 atoms. Why do we see just one atom per water molecule in this structure?
because water have polar covalent bond and only the most electron place is shown in circle. 
not protein and not water and show class 1 HIV drug
licorice fit in to surf_Protein

